### 2015-12-29 fundamentals/examples.tex
line 754: indeed, we did mean figure 3, rather than figure 1. fixed.
clarifies HTC, formats figures for two column layout

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

Early progress has been promising. Many archetypes external to the \Cycamore
library (Table \ref{tab:cycamore}) have been
\cite{huff_streamblender_2014,huff_commodconverter_2014} or are being
\cite{flanagan_bright-lite_2014,skutnik_development_2015,huff_mktdriveninst_2014}
developed for contribution to the \Cyclus ecosystem. These archetypes provide
the first examples of developer-contributed capabilities.  They add to the
fundamental \Cycamore archetypes by providing physics-based reactors,
separations logic, fuel fabrication processing, storage facilities, and expanded
institutional paradigms.  The existence and diversity of these contributed
archetypes illustrate the power and potential of the community-based development
approach that \Cyclus has taken.

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_development_2015} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse
needs of researchers at various institutions. These archetypes, contributed
outside of the \Cyclus core and \Cycamore libraries are the first demonstration
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|X|r|X|}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20$ [MTHM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Recycled Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & offers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table}

@@

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled \gls{MOX} fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation ``equivalence
        method'' originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        \gls{COSI} fuel cycle simulator developed by the French \gls{CEA}.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\textwidth]{./images/flow-mod-open-1.eps}
\end{center}
\caption{1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\textwidth]{./images/flow-closed-1.eps}
\end{center}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\label{fig:flowclosed}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\textwidth]{./images/puseries-1.eps}
\end{center}
\caption{System plutonium buildup with one reactor.}
\label{fig:puseries1}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\textwidth]{./images/puseries-n.eps}
\end{center}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\label{fig:puseriesn}
\end{figure}

>>>>

\begin{table}[H]
\centering
\begin{tabularx}{\columnwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

Early progress has been promising. Many archetypes external to the \Cycamore
library (Table \ref{tab:archetypes}) have been
\cite{huff_streamblender_2014,huff_commodconverter_2014} or are being
\cite{flanagan_bright-lite_2014,skutnik_development_2015,huff_mktdriveninst_2014}
developed for contribution to the \Cyclus ecosystem. These archetypes provide
the first examples of developer-contributed capabilities.  They add to the
fundamental \Cycamore archetypes by providing physics-based reactors,
separations logic, fuel fabrication processing, storage facilities, and expanded
institutional paradigms.  The existence and diversity of these contributed
archetypes illustrate the power and potential of the community-based development
approach that \Cyclus has taken.

\begin{table*}[H]
\centering
\begin{tabularx}{\columnwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_development_2015} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse
needs of researchers at various institutions. These archetypes, contributed
outside of the \Cyclus core and \Cycamore libraries are the first demonstration
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table*}

@@

\begin{table*}[H]
\centering
\begin{tabularx}{\columnwidth}{|X|r|X|}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20$ [MTHM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Spent Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & offers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table*}

@@

    \item \textbf{Spent Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled \gls{MOX} fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation ``equivalence
        method'' originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        \gls{COSI} fuel cycle simulator developed by the French \gls{CEA}.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\columnwidth]{./images/flow-mod-open-1.eps}
\end{center}
\caption{1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\columnwidth]{./images/flow-closed-1.eps}
\end{center}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\label{fig:flowclosed}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\columnwidth]{./images/puseries-1.eps}
\end{center}
\caption{System plutonium buildup with one reactor.}
\label{fig:puseries1}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\columnwidth]{./images/puseries-n.eps}
\end{center}
\caption{System plutonium buildup with staggered refueling for many reactors.}
\label{fig:puseriesn}
\end{figure}

### 2015-12-29 fundamentals/impl.tex
clarifies HTC, formats figures for two column layout

Innovative approaches to designing and optimizing robust fuel cycle strategies can become available by leveraging modern parallel computing resources.  For example, large scale sensitivity analyses to quantify the dependence of fuel cycle outcomes on potentially hundreds of uncertain parameters would only be feasible in a massively parallelized environment.
However, many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits
performance on and compatibility with resource computing infrastructures (e.g. 
cluster or cloud computing). This
constrains the possible scope of simulations and increases the wall-clock time necessary to conduct parameterized sensitivity
analyses and other multi-simulation studies. \Cyclus, on the other hand, is
primarily written in \texttt{C++} and relies on
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms,
which are flexible and support parallelization.
Furthermore, the core infrastructure and related archetypes are free and
open source, BSD-3-clause licensed.  \Cyclus can therefore be easily deployed
on large computer systems, such as \gls{HTC} systems.

Cyclopts \cite{gidden_cyclopts_2015}, a proof-of-principle design and
implementation of a \Cyclus-enabled application on such a large compute system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to study DRE performance and
outcomes. For example, an investigation of the effect of solution degeneracy, a
commonly observed phenomenon in scenarios with individual facilities and basic
(e.g., commodity-only) preference definitions, was performed for three different
fuel cycles: once-through, \gls{MOX} fast reactor-thermal reactor cycles, and
\gls{MOX}-\gls{ThOX} recycle in fast reactors-thermal reactor cycles. Objective
coefficients were generated based on two factors: commodity-facility pairings
and facility location. The population of the possible values of
commodity-facility pairings is always small ($\mathcal{O}(10)$). The size of the
population of possible values of the location effect was investigated for values
of zero, ten, and infinity (i.e., any real number). The study additionally
included an investigation of problem-scaling behavior in order to quantify the
magnitude and rate-of-increase of DRE solution times as a function of the
simulation-entity population for each fuel
cycle\cite{gidden_agent-based_2015}. In total, Cyclopts has run over $10^5$
jobs, comprising more than 60,000 compute hours. The \gls{HTC} infrastructure
has separately been utilized to run and collect information from full \Cyclus
simulations running in parallel on $10^3$ machines reliably for order $10^5$
simulations.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\textwidth]{./images/framework}
\end{center}
\caption{The \Cyclus core provides \glspl{API} that abstract away the details in
the kernel and allow the archetypes to be loaded into the simulation in a modular
fashion.}
\label{fig:framework}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./images/modifiedopen.eps}
\end{center}
\caption{The \Cyclus framework enables fully open, partially open, and fully
closed collaborations\cite{carlsen_cyclus_2014}.}
\label{fig:modifiedopen}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\textwidth]{./images/agent_uml}
\end{center}
\caption{Inheriting \Cyclus class interfaces, such as the \Class{Agent},
\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstracts away
unnecessary details while exposing powerful functionality. In the above
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\textwidth]{./images/compositions}
\end{center}
\caption{
A simple decay line cache holding compositions A, B, C, and a
yet-uncomputed composition D.  B comes from decaying A 1 time step.  C comes
from decaying B 2 time steps, etc.  Black represents the cache for this
particular composition chain. Blue indicates decay operations that can be
satisfied by cache lookups.   If A needs to be decayed 1 time step (A +1), a
quick lookup returns the previously computed B.  Decaying B 3 time steps
requires a decay calculation to compute a new composition D, but subsequent
requests such as decaying A 4 time steps will not require any recalculation.
}
\label{fig:compositions}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
Facility & Reactor$^*$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. It requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple
simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
1.3 are marked with $^*$.}
\label{tab:cycamore}
\end{table}

>>>>

Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that 
limits performance on and compatibility with resource computing infrastructures 
(e.g.  cluster or cloud computing). This constrains the possible scope of 
simulations and increases the wall-clock time necessary to conduct 
parameterized sensitivity analyses and other multi-simulation studies.  For 
example, large scale sensitivity analyses to quantify the dependence of fuel 
cycle outcomes are only feasible in a massively parallelized environment.  
To enable such research, \Cyclus, is primarily written in \texttt{C++} and 
relies on libraries supported by Linux and UNIX (including Ubuntu and OSX) 
platforms, which are flexible and support parallelization.

Cyclopts \cite{gidden_cyclopts_2015}, a proof-of-principle \Cyclus-enabled 
application on such a large compute system,
uses UW-Madison's HTCondor \gls{HTC} infrastructure to study \gls{DRE} performance and
outcomes. For example, an investigation of the effect of solution degeneracy, a
commonly observed phenomenon in scenarios with individual facilities and basic
(e.g., commodity-only) preference definitions, was performed for three different
fuel cycles: once-through, \gls{MOX} fast reactor-thermal reactor cycles, and
\gls{MOX}-\gls{ThOX} recycle in fast reactors-thermal reactor cycles. Objective
coefficients were generated based on two factors: commodity-facility pairings
and facility location. The population of the possible values of
commodity-facility pairings is always small ($\mathcal{O}(10)$). The size of the
population of possible values of the location effect was investigated for values
of zero, ten, and infinity (i.e., any real number). The study additionally
included an investigation of problem-scaling behavior in order to quantify the
magnitude and rate-of-increase of DRE solution times as a function of the
simulation-entity population for each fuel
cycle\cite{gidden_agent-based_2015}. In total, Cyclopts has run over $10^5$
jobs, comprising more than 60,000 compute hours. The \gls{HTC} infrastructure
has separately been utilized to run and collect information from full \Cyclus
simulations running in parallel on $10^3$ machines reliably for order $10^5$
simulations.

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\columnwidth]{./images/framework}
\caption{The \Cyclus core provides \glspl{API} that abstract away the details in
the kernel and allow the archetypes to be loaded into the simulation in a modular
fashion.}
\end{center}
\label{fig:framework}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\columnwidth]{./images/modifiedopen.eps}
\caption{The \Cyclus framework enables fully open, partially open, and fully
closed collaborations\cite{carlsen_cyclus_2014}.}
\end{center}
\label{fig:modifiedopen}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\columnwidth]{./images/agent_uml}
\end{center}
\caption{Inheriting \Cyclus class interfaces, such as the \Class{Agent},
\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstracts away
unnecessary details while exposing powerful functionality. In the above
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\columnwidth]{./images/compositions}
\end{center}
\caption{
A simple decay line cache holding compositions A, B, C, and a
yet-uncomputed composition D.  B comes from decaying A 1 time step.  C comes
from decaying B 2 time steps, etc.  Black represents the cache for this
particular composition chain. Blue indicates decay operations that can be
satisfied by cache lookups.   If A needs to be decayed 1 time step (A +1), a
quick lookup returns the previously computed B.  Decaying B 3 time steps
requires a decay calculation to compute a new composition D, but subsequent
requests such as decaying A 4 time steps will not require any recalculation.
}
\label{fig:compositions}
\end{figure}

@@

\begin{table*}[H]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
Facility & Reactor$^*$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. It requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple
simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
1.3 are marked with $^*$.}
\label{tab:cycamore}
\end{table*}
